\documentclass[11pt,a4paper]{article}
\usepackage{newtxtext,newtxmath}
\usepackage[margin=1in]{geometry}   % 设置边距
\usepackage[utf8]{inputenc}         % 支持 UTF-8
\usepackage[T1]{fontenc}            % 处理字体编码
\usepackage{graphicx}               % 插入图片
\usepackage{setspace}               % 控制行距
\setlength{\parindent}{0pt}         % 段落不缩进
\setlength{\parskip}{0.4em}         % 段间距
\usepackage[hyphens]{url}
\usepackage[colorlinks=true, linkcolor=black, urlcolor=blue, citecolor=black]{hyperref}
\hypersetup{breaklinks=true}
\usepackage{breakurl}
\usepackage{enumitem}
\usepackage[strings]{underscore}

\begin{document}

%-------------------------
% Title and Contact
%-------------------------
\begin{center}
    {\Large \textbf{Xufeng Duan}}\\[6pt]
    \href{mailto:xufengduan@cuhk.edu.hk}{Email} \quad  {\href{https://scholar.google.com/citations?user=W-MI5XUAAAAJ}{Google Scholar}} \quad 
    \href{https://xufengduan.github.io/}{Personal Website}\\
\textbf{Research interests:} Psycholinguistics, Neurolinguistics, Mechanistic Interpretability
\end{center}

%-------------------------
% Working Experience
%-------------------------
\section*{Working Experience}
\vspace{-.5em}
\hrule
\vspace{0.3ex}
\hrule

\textbf{The Chinese University of Hong Kong} \hfill 2025--Present\\
Brain and Mind Institute \hfill \textit{Research Assistant Professor}

%-------------------------
% Education
%-------------------------
\vspace{-1.5em} 
\section*{Education}
\vspace{-.5em} 
\hrule
\vspace{0.3ex}
\hrule
\textbf{The Chinese University of Hong Kong} \hfill 2020--2025\\
Department of Linguistics and Modern Languages \hfill \textit{Ph.D.} in Linguistics

% \textbf{The Chinese University of Hong Kong} \hfill 2019--2020\\
% \href{https://cuhklpl.github.io/}{Department of Linguistics and Modern Languages} \hfill \textit{M.A.} in Linguistics

\textbf{The Chinese University of Hong Kong} \hfill 2019--2020\\
Department of Linguistics and Modern Languages \hfill \textit{M.A.} in Linguistics

\textbf{Sun Yat-sen University} \hfill 2015--2019\\
Neurolinguistics Laboratory \hfill \textit{B.A.} in Chinese

%-------------------------
% Research Projects
%-------------------------
\vspace{-1.5em} 
\section*{Research Projects}
\vspace{-.5em}
\hrule
\vspace{0.3ex}
\hrule

\begin{itemize}[leftmargin=*]
\item Participate, General Research Fund 2021/22 (14613722), \textit{Neurocognitive mechanisms of character amnesia in Chinese handwriting}, RGC, HK\$803,050, 01/01/2023 – 31/12/2025. PI: Zhenguang Cai (CUHK).

\item Participate, Strategic Partnership Award for Research Collaboration, \textit{Chinese handwriting in the digital age: neurocognitive mechanisms of character amnesia}, The Chinese University of Hong Kong, HK\$150,000, 02/2022 – 01/2023. PIs: Zhenguang Cai (CUHK) and Joseph Devlin (UCL).
    
\end{itemize}
%-------------------------
% Publications
%-------------------------
\vspace{-1.5em} 
\section*{Publication}
\vspace{-.5em}
\hrule
\vspace{0.3ex}
\hrule

\hangindent=1.5em \hangafter=1 Tang, X., \textbf{Duan, X.}, \& Cai, Z. G. (2025). Large Language Models for Automated Literature Review: An Evaluation of Reference Generation, Abstract Writing, and Review Composition. \textit{In Proceedings of the 2025 Conference on Empirical Methods in Natural Language Processing (EMNLP), Main Conference}. \href{https://doi.org/10.48550/arXiv.2412.13612}{arXiv:2412.13612}

\hangindent=1.5em \hangafter=1 \textbf{Duan, X.}, Yao, Z., Zhang, Y., Wang, S., \& Cai, Z. G. (2025). How syntax specialization emerges in language models. \textit{arXiv preprint}. \href{https://doi.org/10.48550/arXiv.2505.19548}{
doi:10.48550/arXiv.2505.19548}

\hangindent=1.5em \hangafter=1 Xiao, B., \textbf{Duan, X.}, Haslett, D. A., \& Cai, Z. G. (2025). Human-likeness of LLMs in the Mental Lexicon. \textit{Proceedings of the 29th Conference on Computational Natural Language Learning} (pp. 586–601). Vienna, Austria: Association for Computational Linguistics. \href{https://aclanthology.org/2025.conll-1.38/}{2025.conll-1.38}

\hangindent=1.5em \hangafter=1 Qiu, Z., \textbf{Duan, X.}, \& Cai, Z. G. (2025). Grammaticality representation in ChatGPT as compared to linguists and laypeople. \textit{Humanities and Social Sciences Communications}, 12(1), 1–15. \\
\href{https://doi.org/10.1057/s41599-025-04907-8}{doi:10.1057/s41599-025-04907-8}

\hangindent=1.5em \hangafter=1 Wang, S., \textbf{Duan, X.}, \& Cai, Z. (2025). What to predict? Exploring how sentence structure influences contrast predictions in humans and large language models. In T. Kuribayashi, G. Rambelli, E. Takmaz, P. Wicke, J. Li, \& B.-D. Oh (Eds.), \textit{Proceedings of the Workshop on Cognitive Modeling and Computational Linguistics} (pp. 244–252). NAACL 2025. \href{https://aclanthology.org/2025.cmcl-1.28/}{2025.cmcl-1.28}

\hangindent=1.5em \hangafter=1 Wu, H., \textbf{Duan, X.}, \& Cai, Z. (2025). Distinct social-linguistic processing between humans and large audio-language models: Evidence from model-brain alignment. In T. Kuribayashi, G. Rambelli, E. Takmaz, P. Wicke, J. Li, \& B.-D. Oh (Eds.), \textit{Proceedings of the Workshop on Cognitive Modeling and Computational Linguistics} (pp. 135–143). NAACL 2025. \href{https://aclanthology.org/2025.cmcl-1.18/}{2025.cmcl-1.18}

\hangindent=1.5em \hangafter=1 \textbf{Duan, X.}, Li, S., \& Cai, Z. G. (2025). MacBehaviour: An R package for behavioural experimentation on large language models. \textit{Behavior Research Methods}, 57(1), 19. \href{https://doi.org/10.3758/s13428-024-02524-y}{doi:10.3758/s13428-024-02524-y}

\hangindent=1.5em \hangafter=1 \textbf{Duan, X.}, Zhou, X., Xiao, B., \& Cai, Z. (2025). Unveiling language competence neurons: A psycholinguistic approach to model interpretability. In O. Rambow, L. Wanner, M. Apidianaki, H. Al-Khalifa, B. D. Eugenio, \& S. Schockaert (Eds.), \textit{Proceedings of the 31st International Conference on Computational Linguistics} (pp. 10148–10157). Association for Computational Linguistics. \href{https://aclanthology.org/2025.coling-main.677/}{https://aclanthology.org/2025.coling-main.677}

\hangindent=1.5em \hangafter=1 Zhou, X., Chen, D., Cahyawijaya, S., \textbf{Duan, X.}, \& Cai, Z. G. (2025). Linguistic Minimal Pairs Elicit Linguistic Similarity in Large Language Models. \textit{Proceedings of the 31st International Conference on Computational Linguistics} (pp. 6866–6888). Association for Computational Linguistics. \href{https://aclanthology.org/2025.coling-main.459/}{https://aclanthology.org/2025.coling-main.459}

\hangindent=1.5em \hangafter=1 *Wang, S., \textbf{*Duan, X.}, \& Cai, Z. (2024). A Multimodal Large Language Model “Foresees” Objects Based on Verb Information but Not Gender. \textit{Proceedings of the 28th Conference on Computational Natural Language Learning} (pp. 435–441). \href{https://doi.org/10.18653/v1/2024.conll-1.32}{doi:10.18653/v1/2024.conll-1.32}

\hangindent=1.5em \hangafter=1 Qiu, Z., \textbf{Duan, X.}, \& Cai, Z. (2024). Evaluating Grammatical Well-Formedness in Large Language Models: A Comparative Study with Human Judgments. \textit{Proceedings of the Workshop on Cognitive Modeling and Computational Linguistics} (pp. 189–198). \href{https://doi.org/10.18653/v1/2024.cmcl-1.16}{doi:10.18653/v1/2024.cmcl-1.16}

\hangindent=1.5em \hangafter=1 \textbf{Duan, X.}, Xiao, B., Tang, X., \& Cai, Z. G. (2024). HLB: Benchmarking LLMs' Humanlikeness in Language Use. \textit{arXiv:2409.15890 [cs.CL]}. \href{https://doi.org/10.48550/arXiv.2409.15890}{doi:10.48550/arXiv.2409.15890}

\hangindent=1.5em \hangafter=1 \textbf{Duan, X.}, \& Cai, Z. G. (2024). Chinese Character Processing. \textit{Oxford Research Encyclopedia of Linguistics}. Oxford University Press. \href{https://doi.org/10.1093/acrefore/9780199384655.013.1012}{doi:9780199384655.013.1012}

\hangindent=1.5em \hangafter=1 Wu, H., \textbf{Duan, X.}, \& Cai, Z. G. (2024). Speaker Demographics Modulate Listeners' Neural Correlates of Spoken Word Processing. \textit{Journal of Cognitive Neuroscience}, 36(10), 2208–2226. \href{https://doi.org/10.1162/jocn_a_02225}{doi:10.1162/jocn_a_02225}

\hangindent=1.5em \hangafter=1 Cai, Z., \textbf{Duan, X.}, Haslett, D., Wang, S., \& Pickering, M. (2024). Do large language models resemble humans in language use? \textit{Proceedings of the Workshop on Cognitive Modeling and Computational Linguistics} (pp. 37–56). \href{https://doi.org/10.18653/v1/2024.cmcl-1.4}{doi:10.18653/v1/2024.cmcl-1.4}

\hangindent=1.5em \hangafter=1 Qiu, Z., \textbf{Duan, X.}, \& Cai, Z. (2023). Does ChatGPT Resemble Humans in Processing Implicatures? \textit{Proceedings of the 4th Natural Logic Meets Machine Learning Workshop} (pp. 25–34). \href{https://aclanthology.org/2023.naloma-1.3}{https://aclanthology.org/2023.naloma-1.3}

\hangindent=1.5em \hangafter=1 Lu, S., \textbf{Duan, X.}, \& Li, X. (2021). Prominence and Locality Principle in Chinese Possessive Topicalization Sentences and its Psychological Basis——Evidence from eye-movements. \textit{Contemporary Linguistics}, 23(1), 56–73. \href{https://www.dropbox.com/scl/fi/4ga7a5ssslaed72hx3i2v/Prominence-and-Locality-Principle-in-Chinese-Possessive-Topicalization-Sentences.pdf?rlkey=7rtvpqolr2xs6rtlychdtatwb&st=672mpgkb&dl=0}{[pdf]}


%-------------------------
% Conference Talks
%-------------------------
\vspace{-1.5em} 
\section*{Conference Talk}
\vspace{-.5em}
\hrule
\vspace{0.3ex} 
\hrule

\hangindent=1.5em \hangafter=1 \textbf{Xufeng Duan} (2024). The Neural Basis of Decline in Written Production: Evidence from Chinese Handwriting. \textit{The annual meeting of Society for the Neurobiology of Language (SNL)}, Brisbane, Australia.

\hangindent=1.5em \hangafter=1 \textbf{Xufeng Duan} (2024). MacBehaviour: An R package for behavioural experimentation on large language models. \textit{Architectures and Mechanisms for Language Processing Asia (AMLaP Asia)}, Singapore.

\hangindent=1.5em \hangafter=1 \textbf{Xufeng Duan} (2024). Humanlike language use in LLMs. \textit{CogSci Hong Kong Meetup}, Hong Kong.

\hangindent=1.5em \hangafter=1 \textbf{Xufeng Duan} (2023). Chinese translations of English words: A comparison between human and ChatGPT translations. \textit{Architectures and Mechanisms for Language Processing Asia (AMLaP Asia)}, Hong Kong, China.

\hangindent=1.5em \hangafter=1 Zhenguang Cai, \textbf{Xufeng Duan}, Lu Sun, \& Martin Pickering (2023). Structural priming in ChatGPT. \textit{Architectures and Mechanisms for Language Processing Asia (AMLaP Asia)}, Hong Kong, China.

\hangindent=1.5em \hangafter=1 Zhenguang Cai, \textbf{Xufeng Duan}, David Haslett, Shuqi Wang, \& Martin Pickering (2023). Do language models resemble humans in language use? \textit{Architectures and Mechanisms for Language Processing (AMLaP)}, Donostia-San Sebastián, Spain.

\hangindent=1.5em \hangafter=1 Zhuang Qiu, \textbf{Xufeng Duan}, \& Zhenguang Cai (2023). Does ChatGPT Resemble Humans in Processing Implicatures? \textit{Proceedings of the 4th Natural Logic Meets Machine Learning Workshop}, Nancy, France.

\hangindent=1.5em \hangafter=1 \textbf{Xufeng Duan} (2018). Language rehabilitation training therapies for Chinese aphasia — Using Chinese characters as clues. \textit{Beyond A Limited Scope: Chinese for Specific, Academic, \& Professional Purposes}, Hawaii, US.

\hangindent=1.5em \hangafter=1 \textbf{Xufeng Duan} (2018). The Dependence on different symbolic systems during word recognition-pronunciation tests by Chinese native speakers with aphasia — based on eye-movement methodology. \textit{Annual Conference of the Chinese Society of Neurological Linguistics}, Xuzhou, China.

\hangindent=1.5em \hangafter=1 \textbf{Xufeng Duan} (2018). The Rules of Prominency and Locality Psychological Reality Basis. \textit{Annual Academic Conference of the Chinese Linguistic Society}, Guangzhou, China.

%-------------------------
% Poster Presentations
%-------------------------
\vspace{-1.2em} 
\section*{Poster Presentation}
\vspace{-.5em} 
\hrule
\vspace{0.3ex}
\hrule

\hangindent=1.5em \hangafter=1 Zhang, Y., \textbf{Duan, X.}, \& Cai, Z. (2024). The causal role of left inferior frontal gyri in Chinese character handwriting: A transcranial magnetic stimulation study. \textit{The annual meeting of Society for the Neurobiology of Language (SNL)}, Brisbane, Australia.

\hangindent=1.5em \hangafter=1 Qiu, Z., \textbf{Duan, X.}, \& Cai, Z. (2024). Do Large Language Models Resemble Humans in Grammaticality Judgement? \textit{Human sentence processing 2024}, University of Michigan, USA.

\hangindent=1.5em \hangafter=1 \textbf{Duan, X.}, Cai, Z., \& Yao, B. (2023). Electrophysiological responses associated with character amnesia in Chinese handwriting. \textit{Architectures and Mechanisms for Language Processing (AMLaP)}, Donostia-San Sebastián, Spain.

\hangindent=1.5em \hangafter=1 Wu, H., \textbf{Duan, X.}, \& Cai, Z. (2023). Belief of Speakers’ Linguistic Competence Modulates the N400 Effect Elicited by Inconsistent Lexical Use. \textit{Architectures and Mechanisms for Language Processing (AMLaP)}, Donostia-San Sebastián, Spain.

\hangindent=1.5em \hangafter=1 Qiu, Z., \textbf{Duan, X.}, Cai, Z., \& Zhao, N. (2023). Pragmatic Implicature Processing in ChatGPT. \textit{Architectures and Mechanisms for Language Processing (AMLaP)}, Donostia-San Sebastián, Spain.

% %-------------------------
% % Awards and Scholarships
% %-------------------------
% \section*{Scholarship and Research Funding}
% \hrule
% \vspace{0.3ex}
% \hrule
% \begin{itemize}[leftmargin=*, labelsep=0.5em]
%     \item The Chinese University of Hong Kong Ph.D. Studentship \hfill \textbf{880,000 HKD, 2020-2024}
%     \item Key Laboratory Open Fund for student \hfill \textbf{30,000 RMB, 2019} \\ \textit{Multimodal (EEG/fNIRs/Eyetracking) Corpus for Special Population}, Sun Yat-sen University.
% \end{itemize}

%-------------------------
% Training / Internship
%-------------------------
\vspace{-1.2em} 
\section*{Training and Internship}
\vspace{-.5em} 
\hrule
\vspace{0.3ex}
\hrule
\begin{itemize}[leftmargin=*, labelsep=0.5em]
    \item \textbf{TMS Training}\hfill May 2023\\ APAC TMS clinic Workshop, University of Numnich \& MagMore Company.
    \item \textbf{Language Therapist} \hfill Jul. 2017 -- Jul. 2019\\ The Third Affiliated Hospital of Sun Yat-sen University.
\end{itemize}

\vspace{-2.5em} 
\section*{Skill}
\vspace{-.5em} 
\hrule
\vspace{0.3ex}
\hrule
\begin{itemize}[leftmargin=*, labelsep=0.5em]
    \item \textbf{LLMs}: Mechanistic interpretability, Model fine-tuning, Benchmark Construction, etc.
    \item \textbf{Experimentation:} fMRI / TMS / EEG / fNIRS / Eye-tracker using PsychoPy \& Experiment Builder \& E-prime \& Gorilla / Qualtrics.
    \item \textbf{Coding:} Python, R and Matlab.
\end{itemize}
\vspace{-1em} 

\centering \textbf{Last updated:} 21/08/2025

\end{document}


